Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-08-08 response.tex

\item The authors provide also state level predictions. However, I do not see 
where a spatial component is included in the model. Is this only via P or are 
all states just modelled independently. For influenza I would think that it 
might be reasonable to assume that neighbouring states show similar behaviour 
in both ILI and hosptialisation so that borrowing strength between states 
within one model seems sensible. Please discuss.

\spencer{Yes, borrowing strength between states would be reasonable, but 
fitting such a model would likely take much more time than was give by FluSight
to produce forecasts. In the revised manuscript, after defining the ILI model
we state:

``Model (\ref{eq:ili_model}) was fit 
independently for each location. This decision was made largely due to the 
limited time given by FluSight to produce forecasts. That is,
during the competition, data were typically released on Wednesday afternoons and
forecasts were due by the evening of the same day giving only a few hours to 
produce forecasts. A natural extension of the model would be to allow for states
to borrow information from neighboring states." ??Add something to discussion}

@@

\subsection*{Specific comments:}

\begin{enumerate}[-]

\item Section 2, page 3: please be more clear on what you mean by the 
"first seven season". Provide a time frame.

\spencer{The ``first seven seasons" was replaced with 
`` the first seven seasons, 2013 to 2019,".}

@@

https://hafen.github.io/geofacet/

I could image that the curves, onset and general behaviour, varies across the 
states. The authors refer to this a bit in the discussion. In addition I would 
prefer to also have months names in the axis labels, to avoid confusion that 
week 1 is not the first week in January.

Can the hospitalization figures also be shown on state level at least in an appendix.

\spencer{I made the changes to the x-axes so that they are labeled by date, 
listed as month, rather than by week. I also added in the 
supplementary material the geofacet plots showing 
ILI and hospitalizations for each state organized by geographic location. Some
discussion about the relation between neighboring states is made there.}

@@

\item Section 3.5: Please be clear what the strength of a Bayesian inference scheme is.

\item Equation 6): What does the tilde mean?

\spencer{In the revised manuscript we state:

``Here $\widetilde{ILI}_{s,w + i}$ represents the 
predicted or forecast ILI at $i$ weeks in the future."}

@@

\item Page 11: Please motivate the choice of an autoregressive process of order 1 
more clearly. Why not use a higher order? Would this be beneficial?

\spencer{We explored higher orders and found that they didn't provide any more
predictive power than order 1 did. See our response to your general comment 3.}

@@

\item Page 14: Please discuss the assumption that all components of $\alpha_s$ and 
$\sigma_\epsilon^2$ are assumed to be same across all seasons. Is this realistic?

\spencer{We do not generally make this assumption in our model. The only time
we make this assumption is when modeling log-hospitalizations instead of 
hospitalizations and then we do it becuase otherwise the predictive variance
was unreasonably large for lack of hospitalization data.
Where this is pertinent in the supplementary materials, we note ??.
In the simulation study,
we simulate hospitalization data which we attempt to forecast for each left
out season in the leave one season out scheme. For clarification, we added 
the following.

``Note that this is not
a model assumption we make but only a simplyfying assumption for simiulating
the data."}

@@

\item Figure 7: Please make clear in the caption what the columns represent in an 
intuitive manner.

\spencer{In the updated manuscript, this figure was replaced with another figure
which included 3 plots we believe is much more intuitive and descriptive than
the original figure. The title of the new figure remains ``figure 7" and 
the caption is hopefully understandable.}

@@

\item Equation 11, 12, 13, 14: Please motivate. The authors write in Section 3.4 
that the modelling of discrepancy might require careful selection of priors. 
Please underline more how this is taken care of in this manuscript.

\spencer{We decided to put equations 11 - 14 in the supplementary materials, and
give more of an over description of the prior distributions in section 3.6. Here
is one updated paragraph describing how a prior distribution was assigned to
improve identifiability issues introduced by including discprepancy modeling.

``Additional prior constraints were made to improve parameter identifiability. 
Just as was done in Osthus et al. \cite[]{osthus2019dynamic},
we set the initial value of the 
susceptible population compartment of the SIR model was set to $S_0 = 0.9$. 
The parameters $I_{0s}$, $\beta_s$, and $\rho_s$ were assigned informative 
priors. In a previous version of this manuscript, when fitting an ASG model
with discrepancy components,
rather than estimating all parameters in a Bayesian way,
we set the parameter $\lambda_s$ from (\ref{eq:asg_function_rep})
to be equal to its MLE. In this updated manuscript, 
however, we use empirical Bayes and center the first component of the 
hierarichal prior $\theta$ to be the mean of MLEs for $\lambda_s$ across
all seasons and set the variance parameter so the prior was tight around the
mean."}
